\begin{thebibliography}{99}

\bibitem{BLAS1}
    C. L. Lawson, R. J. Hanson, D. Kincaid, and F. T. Krogh, Basic Linear Algebra Subprograms for FORTRAN
    usage, ACM Trans. Math. Soft., 5 (1979), pp. 308—323.

\bibitem{BLAS2}
    J. J. Dongarra, J. Du Croz, S. Hammarling, and R. J. Hanson, An extended set of FORTRAN Basic Linear
    Algebra Subprograms, ACM Trans. Math. Soft., 14 (1988), pp. 1—17.

\bibitem{BLAS3}
    J. J. Dongarra, J. Du Croz, S. Hammarling, and R. J. Hanson, Algorithm 656: An extended set of FORTRAN
    Basic Linear Algebra Subprograms, ACM Trans. Math. Soft., 14 (1988), pp. 18—32.

\bibitem{BLAS4}
    J. J. Dongarra, J. Du Croz, I. S. Duff, and S. Hammarling, A set of Level 3 Basic Linear Algebra
    Subprograms, ACM Trans. Math. Soft., 16 (1990), pp. 1—17.

\bibitem{BLAS5}
    J. J. Dongarra, J. Du Croz, I. S. Duff, and S. Hammarling, Algorithm 679: A set of Level 3 Basic Linear
    Algebra Subprograms, ACM Trans. Math. Soft., 16 (1990), pp. 18—28.

\bibitem{lapack}
    {Anderson, E. and Bai, Z. and Bischof, C. and Blackford, S. and Demmel, J. and Dongarra, J. and
    Du Croz, J. and Greenbaum, A. and Hammarling, S. and McKenney, A. and Sorensen, D.},
    {{LAPACK} Users' Guide}, {Society for Industrial and Applied Mathematics}, {1999}.

\bibitem{suitesparse}
    Algorithm 907: KLU, A Direct Sparse Solver for Circuit Simulation Problems, Timothy A. Davis, Ekanathan
    Palamadai Natarajan, ACM Transactions on Mathematical Software, Vol 37, Issue 6, 2010, pp 36:1 -
    36:17.

\bibitem{suitesparse2}
    Algorithm 915, SuiteSparseQR: Multifrontal multithreaded rank-revealing sparse QR factorization, Timothy
    A. Davis, ACM Transactions on Mathematical Software, Vol 38, Issue 1, 2011, pp 8:1 - 8:22.

\bibitem{petsc-web-page}
    {Satish Balay,  Shrirang Abhyankar,  Mark~F. Adams,  Jed Brown,  Peter Brune,  Kris Buschelman,  Lisandro
        Dalcin,  Alp Dener,  Victor Eijkhout,  William~D. Gropp,  Dinesh Kaushik,  Matthew~G. Knepley,
        Dave~A. May, Lois Curfman McInnes, Richard Tran Mills, Todd Munson,  Karl Rupp,  Patrick Sanan,
        Barry~F. Smith,  Stefano Zampini,  Hong Zhang,  Hong Zhang}, {{PETS}c {W}eb page},
        {http://www.mcs.anl.gov/petsc}, year = {2018}.

\bibitem{petsc-user-ref}
    {Satish Balay,  Shrirang Abhyankar,  Mark~F. Adams,  Jed Brown,  Peter Brune,  Kris Buschelman,  Lisandro
        Dalcin,  Alp Dener,  Victor Eijkhout,  William~D. Gropp,  Dinesh Kaushik,  Matthew~G. Knepley,
        Dave~A. May,  Lois Curfman McInnes,  Richard Tran Mills,  Todd Munson,  Karl Rupp,  Patrick Sanan,
        Barry~F. Smith,  Stefano Zampini,  Hong Zhang,}, {{PETS}c Users Manual}, {Argonne National
        Laboratory}, {ANL-95/11 - Revision 3.9}, 2018.

\bibitem{petsc-efficient}
    Satish Balay,  William D. Gropp, Lois Curfman McInnes,  Barry F. Smith,
    Efficient Management of Parallelism in Object Oriented Numerical Software Libraries,
    Modern Software Tools in Scientific Computing, Birkh{\"{a}}user Press,
    1997, 163--202.

\bibitem{mumps}
    P. R. Amestoy, A. Buttari, J.-Y. L'Excellent and T. Mary, On the complexity of the Block Low-Rank
    multifrontal factorization, SIAM Journal on Scientific Computing, volume 39, number 4, pages
    A1710-A1740.

\bibitem{li05}
    {Xiaoye S. Li}, {An Overview of {SuperLU}: Algorithms, Implementation, and User Interface},
    toms, 31(3), {2005}, {302-325}.

\bibitem{superlu_ug99}
     {X.S. Li and J.W. Demmel and J.R. Gilbert and iL. Grigori and M. Shao and I. Yamazaki},
     {{SuperLU Users' Guide}}, {Lawrence Berkeley National Laboratory},
     {LBNL-44289}, {September}, {1999}.

\bibitem{superlu99}
    {James W. Demmel and Stanley C. Eisenstat and John R. Gilbert and Xiaoye S. Li and Joseph W. H. Liu},
    {A supernodal approach to sparse partial pivoting}, {SIAM J. Matrix Analysis and Applications},
    20(3), {1999}, {720-755}.

\bibitem{sxamg-library}
    Hui Liu, SXAMG: a Serial Algebraic Multigrid Solver Library, 2018.

\bibitem{fasp}
    Xiaozhe Hu, Wei Liu, Guan Qin, Jinchao Xu, Zhensong Zhang,
    Development of A Fast Auxiliary Subspace Pre-conditioner for Numerical Reservoir Simulators,
    SPE-148388-MS, SPE Reservoir Characterisation and Simulation Conference and Exhibition, 9-11 October, Abu Dhabi, UAE.

\end{thebibliography}
