
\documentclass[12pt]{book}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}

\usepackage[ruled]{algorithm2e}

\usepackage{fancyheadings}
\usepackage{setspace}
\usepackage{color}
\usepackage{caption}
\usepackage{float}
\usepackage{fancyvrb}
\usepackage{graphicx}
\usepackage{makeidx}
\usepackage{listings}
\usepackage{float}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{lipsum}
\usepackage{imakeidx}
\usepackage[bookmarksnumbered=true,colorlinks=true,linkcolor=blue]{hyperref}

\textwidth=17cm
\textheight=22.5cm

\setlength{\oddsidemargin}{-0.1in}
\setlength{\evensidemargin}{-0.1in}

\topmargin=3pt
\abovecaptionskip=3pt
\belowcaptionskip=3pt


\marginparwidth 0pt \marginparsep 10pt
\columnsep 0.5in \parindent  18pt   \parskip  0pt
\setlength{\itemsep}{.5pt}
\setlength{\parsep}{0pt}
\setlength\parindent{0pt}
\setcounter{secnumdepth}{4}

\definecolor{verbgray}{gray}{0.9}

\lstnewenvironment{evb}{%
      \lstset{backgroundcolor=\color{verbgray},
        frame=single, framerule=0pt, basicstyle=\small\ttfamily,belowskip=0.3cm,
              columns=fullflexible, keepspaces=true}}{}

\definecolor{shadecolor}{rgb}{.9, .9, .9}

%%%%%% nverb
\lstset{
        basicstyle=\color{blue} \ttfamily,
}
\lstdefinestyle{inline}{
    columns=fullflexible,breaklines=true,
}
\newcommand{\vb}[1]{\lstinline[style=inline]!#1!}

\pagestyle{fancy}

\fancyhead[RE]{\leftmark}
\fancyhead[LO]{\rightmark}
\fancyhead[LE,RO]{}
\renewcommand\sectionmark[1]{\markright{\thesection.\ #1}}

\makeindex

\begin{document}

\begin{titlepage}
\begin{center}

\vspace{5cm}
\begin{spacing}{2.5}
\vspace{5cm}
\textbf{} \\[1.5cm]
\textbf{\Huge SLSPack: an Interface Library for Sparse Linear Solver Packages} \\[0.5cm]
\textbf{VERSION 1.0}
\vspace*{\fill}
\end{spacing}

\begin{spacing}{1.15}
\textnormal{\large Hui Liu \\
    2018}
\end{spacing}
\end{center}
\end{titlepage}

\tableofcontents

\setlength{\parskip}{8pt}

\clearpage
\pagenumbering{arabic}

\input{intro}
\input{install}
\input{mv}
\input{solver}
\input{utils}
\input{ref}

\appendix

\chapter{Optional Packages}

\section{BLAS}
The BLAS (Basic Linear Algebra Subprograms) are routines that provide standard building blocks for performing basic vector and matrix operations. The Level 1 BLAS perform scalar, vector and vector-vector operations, the Level 2 BLAS perform matrix-vector operations, and the Level 3 BLAS perform matrix-matrix operations. Because the BLAS are efficient, portable, and widely available, they are commonly used in the development of high quality linear algebra software, LAPACK for example.

Official website: \url{http://www.netlib.org/blas/}

BLAS search directories:
\begin{evb}
/usr/local/lib
/usr/local/lib64
/usr/local/blas/lib
/usr/local/blas*/lib
/usr/local/blas/
/usr/local/blas*/
/usr/lib
/usr/lib64
/opt/blas/lib
/opt/blas*/lib
\end{evb}

\section{LAPACK}
LAPACK is written in Fortran 90 and provides routines for solving systems of simultaneous linear equations, least-squares solutions of linear systems of equations, eigenvalue problems, and singular value problems. The associated matrix factorizations (LU, Cholesky, QR, SVD, Schur, generalized Schur) are also provided, as are related computations such as reordering of the Schur factorizations and estimating condition numbers. Dense and banded matrices are handled, but not general sparse matrices. In all areas, similar functionality is provided for real and complex matrices, in both single and double precision.

Official website: \url{http://www.netlib.org/lapack/}

LAPACK search directories:
\begin{evb}
/usr/local/lib
/usr/local/lib64
/usr/local/lapack/lib
/usr/local/lapack*/lib
/usr/local/lapack/
/usr/local/lapack*/
/usr/lib
/usr/lib64
/opt/lapack/lib
/opt/lapack*/lib
\end{evb}

\section{LASPack}
LASPack is a package for solving large sparse systems of linear equations like those which arise from discretization of partial differential equations.  It contains classical as well as selected state-of-the-art algorithms which are commonly used for large sparse systems such as CG-like methods for non-symmetric systems (CGN, GMRES, BiCG, QMR, CGS, and BiCGStab) and multilevel methods such as multigrid and conjugate gradient method preconditioned by multigrid and BPX preconditioners.  LASPack is written in ANSI C and is thus largely portable.  

Official website: {\small \url{http://www.netlib.org/utk/misc/sw_survey/urc/html/LASPack.1.html}}

LASPack search directories (include and lib):
\begin{evb}
/usr/local/laspack/
/usr/local/laspack*/
/usr/local/
/usr/
/opt/laspack/
/opt/laspack*
\end{evb}
The include and lib directories are sub-directories of above directories, such as /usr/local/laspack/include and /usr/local/laspack/lib. Users can also set customized directories with options: --with-laspack-libdir=DIR and --with-laspack-incdir=DIR.

\section{SuiteSparse}
A Suite of Sparse matrix software, including UMFPACK, CHOLMOD, SPQR, KLU, BTF, and ordering methods (AMD, CAMD, COLAMD, and CCOLAMD). 

Official website: \url{https://github.com/jluttine/suitesparse} 

Official website: \url{http://www.suitesparse.com}

SuiteSparse search directories:
\begin{evb}
/usr/local/SuiteSparse
/usr/local/SuiteSparse*
/usr/local
/usr
/opt/SuiteSparse 
/opt/SuiteSparse*
\end{evb}

The include and lib directories are sub-directories of above directories. Users can also set customized directories with options.

\section{MUMPS}
MUMPS (MUltifrontal Massively Parallel sparse direct Solver) is a software application for the solution of large sparse systems of linear algebraic equations on distributed memory parallel computers. It was developed in European project PARASOL (1996–1999) by CERFACS, IRIT-ENSEEIHT and RAL. The software implements the multifrontal method, which is a version of Gaussian elimination for large sparse systems of equations, especially those arising from the finite element method. It is written in Fortran 90 with parallelism by MPI and it uses BLAS and ScaLAPACK kernels for dense matrix computations. Since 1999, MUMPS has been supported by CERFACS, IRIT-ENSEEIHT, and INRIA. 

Official website: \url{http://mumps.enseeiht.fr/}

MUMPS search directories:
\begin{evb}
/usr/local/mumps-seq/
/usr/local/mumps*-seq/
/usr/local/
/usr/
/opt/mumps-seq/
/opt/mumps*-seq/
\end{evb}

The include and lib directories are sub-directories of above directories. Users can also set customized directories with options.

\section{PETSC}
PETSc, pronounced PET-see (the S is silent), is a suite of data structures and routines for the scalable (parallel) solution of scientific applications modeled by partial differential equations. It supports MPI, and GPUs through CUDA or OpenCL, as well as hybrid MPI-GPU parallelism. PETSc is intended for use in large-scale application projects, many ongoing computational science projects are built around the PETSc libraries. PETSc is easy to use for beginners. Moreover, its careful design allows advanced users to have detailed control over the solution process. PETSc includes a large suite of parallel linear, nonlinear equation solvers and ODE integrators that are easily used in application codes written in C, C++, Fortran and now Python. PETSc provides many of the mechanisms needed within parallel application codes, such as simple parallel matrix and vector assembly routines that allow the overlap of communication and computation. In addition, PETSc includes support for parallel distributed arrays useful for finite difference methods. 

Official website: \url{https://www.mcs.anl.gov/petsc/}

PETSC search directories:
\begin{evb}
/usr/local/petsc-seq
/usr/local/petsc*-seq/
/opt/petsc-seq/
/opt/petsc*-seq/
\end{evb}

The include and lib directories are sub-directories of above directories. Users can also set customized directories with options.

\section{LIS}
Lis (Library of Iterative Solvers for linear systems, pronounced [lis]) is a parallel software library for solving linear equations and eigenvalue problems that arise in the numerical solution of partial differential equations using iterative methods.

Official website: \url{http://www.ssisc.org/lis/}

LIS search directories:
\begin{evb}
/usr/local/lis
/usr/local/lis*
/usr/local
/usr
/opt/lis 
/opt/lis*
\end{evb}

The include and lib directories are sub-directories of above directories. Users can also set customized directories with options.

\section{FASP}
FASP team plans to construct a pool of discrete problems arising from partial differential equations (PDEs) or PDE systems and efficient linear solvers for these problems. They mainly utilize the methodology of Auxiliary Space Preconditioning (ASP) to construct efficient linear solvers. A set of Krylov solvers and AMG solvers have been implemented. 

Official website: \url{http://fasp.sourceforge.net/}

FASP search directories:
\begin{evb}
/usr/local/fasp
/usr/local/fasp*
/usr/local
/usr
/opt/fasp 
/opt/fasp*
\end{evb}
The include and lib directories are sub-directories of above directories. Users can also set customized directories with options.

\section{SUPERLU}
SuperLU is a general purpose library for the direct solution of large, sparse, nonsymmetric systems of linear equations on high performance machines. The library is written in C and is callable from either C or Fortran. The library routines will perform an LU decomposition with partial pivoting and triangular system solves through forward and back substitution. The LU factorization routines can handle non-square matrices but the triangular solves are performed only for square matrices.

Official website: \url{http://crd-legacy.lbl.gov/~xiaoye/SuperLU/}

SUPERLU search directories:
\begin{evb}
/usr/local/superlu
/usr/local/superlu*
/usr/local
/usr
/opt/superlu 
/opt/superlu*
\end{evb}

The include and lib directories are sub-directories of above directories. Users can also set customized directories with options.

\section{PARDISO}
The package PARDISO is a thread-safe, high-performance, robust, memory efficient and easy to use software for solving large sparse symmetric and unsymmetric linear systems of equations on shared-memory and distributed-memory multiprocessors. 

Official website: \url{http://www.pardiso-project.org/}

PARDISO search directories:
\begin{evb}
/usr/local/intel
/opt/intel

/usr/local/pardiso
/usr/local/pardiso*
/usr/local/lib
/usr/local/lib64 
/usr/lib
/usr/lib64
/opt/pardiso
/opt/pardiso*
\end{evb}

\section{HSL MI20 (AMG)}
An AMG package using classical method. 

Official website: \url{http://www.hsl.rl.ac.uk/catalogue/hsl_mi20.html}

HSL MI20 search directories:
\begin{evb}
/usr/local/hsl_mi20
/usr/local/hsl_mi20*
/opt/hsl_mi20
/opt/hsl_mi20*
\end{evb}

\section{SXAMG}
An AMG package using classical method. 

Official website: \url{https://github.com/huiscliu/sxamg/}

SXAMG search directories:
\begin{evb}
/usr/local/sxamg
/usr/local/sxamg*
/opt/sxamg
/opt/sxamg*
\end{evb}

The include and lib directories are sub-directories of above directories. Users can also set customized directories using options.

\end{document}
